Meta-analysis

### 2019-11-11 04_Prep_data.Rmd
Adding replicates to the slim datasets
Impute missing yield variances, correct slimmer spelling from slimer

@@

slimer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
               slim_PM_dat$spray_management != "Early_plus",]

write.csv(slimer_PM_dat, file = "data/slimer_PM_clusterdat.csv", row.names = FALSE)
```

>>>>

table(slim_PM_dat$spray_management)
sum(table(slim_PM_dat$spray_management)[1:7])
nrow(slim_PM_dat)

@@

slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
               slim_PM_dat$spray_management != "Early_plus",]

write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

### 2019-11-11 05_MetaAnalysis.Rmd
Impute missing yield variances, correct slimmer spelling from slimer

```{r LME_slimer_cluster_disease_mod}
slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")

m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model

@@

>>>>

```{r LME_slimmer_cluster_disease_mod}
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")

m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
              (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
           data = slimmer_PM_dat)

anova(m8,m9) # m9 is significantly better model
anova(m9,m10) # m9 is significantly better model

@@

```{r}
library(metafor)
sum(is.na(slimmer_PM_dat$yield_error)) # 14 treatments have no error
sum(!is.na(slimmer_PM_dat$yield_error)) # 152 treatments with error

hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed

# generate yield error values
log_Yerror <- rnorm(14, mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
                    sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))

# Lets plot the values to see if they are significantly different
# First lets convert Variance to standard error for all the variables that have variance recorded
slimmer_PM_dat$yield_SE <- sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)

# Second; adding the imputed standard errors
slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <- sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"]) # 14 treatments have no error

# Plot the imputed errors for each trial
slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
   ggplot(aes(y = grain_yield.t.ha, trial))+
   #geom_point()+
   geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                  ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                  position = "jitter"
                 )+
   ylim(0.2,1.5)

# all errorbars shoul overlap so they are consistant with the meta-data describing no significant difference bettween treatments
# lets test to make sure
if(max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             FUN = "-")) > 0){
   message("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk")
}else{
                message("\nImputed variances show no significant distances :)\n Now adding variances to data")
   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
       }

slimmer_PM_dat$yield_error

slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha*1000)
slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)

table(slimmer_PM_dat$spray_management)

PM_mv_AI <- rma.mv(yi,log(yield_error*1000),
 #                  mods = spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial_ref),
                   struct = "UN",
                   data = slimmer_PM_dat)

PM_mv_AI

anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
                          c(0,0,-1,1,0),
                          c(0,0,-1,0,1),
                          c(0,0,0,-1,1)))

There are outcomes with non-positive sampling variances.Negative sampling variances constrained to zero.'V' appears to be not positive definite.Some combinations of the levels of the inner factor never occurred. Corresponding rho value(s) fixed to 0.diag(.) had 0 or NA entries; non-finite result is doubtfulError in .ll.rma.mv(opt.res$par, reml = reml, Y = Y, M = V, A = A, X.fit = X,  : 
  Final variance-covariance matrix not positive definite.

There are outcomes with non-positive sampling variances.Negative sampling variances constrained to zero.'V' appears to be not positive definite.Some combinations of the levels of the inner factor never occurred. Corresponding rho value(s) fixed to 0.diag(.) had 0 or NA entries; non-finite result is doubtfulError in .ll.rma.mv(opt.res$par, reml = reml, Y = Y, M = V, A = A, X.fit = X,  : 
  Final variance-covariance matrix not positive definite.
```
